---
title: "tidy_tuesday_1"
author: "Ishwara Hegde"
date: "7/15/2020"
output: html_document
---
For my first Tidy Tuesday I wish to analyze how the proportion of astronauts have varied over time. 
I mainly focus on the USA and U.S.S.R/ Russia. This is because I want to keep things simple and use only three factors levels.  
```{r setup, include=FALSE}
#Installing necessary packages

#Uncomment the next line if you do not have bbplot
#devtools::install_github('bbc/bbplot')
knitr::opts_chunk$set(echo = TRUE)
# Setting My working directory. please change as required
#setwd("C:\\Users\\user\\OneDrive - City University of Hong Kong\\University\\Cemfi")
if(!require(pacman))install.packages("pacman")

pacman::p_load('dplyr', 'tidyr', 'gapminder',
               'ggplot2',  'ggalt',
               'forcats', 'R.utils', 'png', 
               'grid', 'ggpubr', 'scales',
               'bbplot', 'knitr', 'janitor', 'tidyverse')


#Loading the required data
astronauts <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-07-14/astronauts.csv')


```
I will use the cleaning script already provided. In the future, I will hopefully be able to clearn the data myself.
```{r, data cleaning}
astronauts <-astronauts %>% 
  clean_names() %>% 
  filter(!is.na(number)) %>%  # remove last row (all values are NA)
  mutate(
    sex = if_else(sex == "M", "male", "female"),
    military_civilian = if_else(military_civilian == "Mil", "military", "civilian")
  )
```

The main goal for my analysis is to describe graphically the nationalities of astronauts over time. 

```{r, data analysis}
# I will find the number of unique nationalities below 
nations<-unique(astronauts$nationality)
nations

# There are 40 unique nations. Below I will convert nationalities to factors 
astronauts<-astronauts %>% mutate(fct_nations=factor(nationality,levels=nations))
# I will create a grouped data set of astronauts by nationality and year of mission
data1<-astronauts %>% group_by(nationality,year_of_mission) %>% summarise(n=n()) %>%arrange(year_of_mission)

```
For plotting I use the BBC Journalism team's tutorials.
```{r, Plot}
# I want to plot by year the nationalities 

stacked_bars <- ggplot(data = data1, 
                       aes(x = year_of_mission,
                           y = n,
                           fill = fct_lump(nationality,n=2))) +
  geom_bar(stat = "identity", 
           position = "fill") +
  bbc_style() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_viridis_d(direction = -1) +
  geom_hline(yintercept = 0, size = 1, colour = "#333333") +
  labs(title = "Nationalities of Astronauts") +
  theme(legend.position = "top", 
        legend.justification = "left") +
  guides(fill = guide_legend(reverse = TRUE))

# Exporting the graph
ggsave(
  "stacked_bars.png",
  plot = last_plot(),
  device = "png",
  scale = 1,
  width = NA,
  height = NA,
  units = c("in", "cm", "mm"),
  dpi = 300)


```
